Defficiency Screen Functional Analysis

### 2023-07-10 DeficiencyScreen/GO_Analysis.Rmd
update

kegg=keggLink("pathway","dme")
names(kegg)=gsub("dme:Dmel_","",names(kegg))

##i=1
##kegg.names=unique(substr(kegg,6,13))
##names(kegg.names)=as.vector(kegg.names)
##while(i<=length(kegg.names)){
##  kegg.names[i] <- strsplit(keggGet(kegg.names[i])[[1]]$NAME," - ")[[1]][1]
##  i=i+1
##}

@@

temp = setNames(GeneIDKey$Symbol, GeneIDKey$CG)
temp = temp[intersect(names(kegg),names(temp))]
kegg = kegg[intersect(names(kegg),names(temp))]
names(kegg) = temp[names(kegg)]
kegg = as.list(kegg)
keggID=keggConv("dme","ncbi-geneid")

@@

Moderate.GO = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/ModerateGOAnalysis.csv", row.names = 1)
Strong.GO = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/RStrongGOAnalysis.csv", row.names = 1)

@@

@@

GO.data = Repress.GO[Repress.GO$adjp <= .05 &
                     Repress.GO$ontology == 'BP',
                     c("category", "term","adjp", "numDEInCat", "numInCat")]

go_analysis = GO.data$category
scores = setNames(-log10(GO.data$adjp), go_analysis)

##simMatrix <- calculateSimMatrix(go_analysis,
##                                orgdb="org.Dm.eg.db",
##                                ont="BP",
##                                method="Rel")

@@

##reducedTerms <- reduceSimMatrix(simMatrix,
##                                scores,
##                                threshold=0.7,
##                                orgdb="org.Dm.eg.db")
##write.csv(reducedTerms,"/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/Repressor.BP.reducedTerms.csv")

simMatrix = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/Repressor.BP.simMatrix.csv", row.names = 1)
reducedTerms = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/Repressor.BP.reducedTerms.csv", row.names = 1)

data = GO.data[,c("term","adjp","numDEInCat", "numInCat", "category")]
data = data[order(data$adjp, decreasing = T),]
data$Score = -log10(data$adjp)
data$term = factor(data$term, levels = c(unique(data$term)))

fig <- plot_ly(data, 
               x = ~numDEInCat, y = ~term, 
               type = 'bar',
               name = "term",
               marker = list(colorscale = list(c(0,.5,1), c("brown","gold", "steelblue")),
    reversescale =T,
                             colorbar = list(title = "-log10(FDR)",
                                      len = .8, outlinewidth = 0,
                                      tickformat = ".2f",
                                      tick0 = 0),##, dtick = .01),
                             color = ~Score,
                             line = list(color = "black", width = 1.5)),
    hoverinfo = "text",
    hovertext = paste("Sample:", data$term,
                      "\nGO ID: ", data$category,
                      "\nTotal DE: ", data$numDEInCat,
                      "\nTotal in Cat.: ", data$numInCat,
                      "\nFDR: ", signif(data$adjp, 3))) %>%
    layout(xaxis = list(title = "Number of Genes"),
           yaxis = list(title = ""),
           title = "Significantly Enriched GO term Summary",
           margin = m)

>>>>

@@

keggID=keggConv("dme","ncbi-geneid")

kegg = readRDS("/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/kegg.symbol2path.RData")

@@

Moderate.GO = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/ModerateGOAnalysis.csv", row.names = 1)
Strong.GO = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/StrongGOAnalysis.csv", row.names = 1)

@@

GO.data = Moderate.GO
GO.data = GO.data[GO.data$ontology == 'BP',
                  c("category", "term","adjp", "numDEInCat", "numInCat")]

data = GO.data[20:1,c("term","adjp","numDEInCat", "numInCat", "category")]
data$Score = -log10(data$adjp)
data$term = factor(data$term, levels = c(unique(data$term)))

fig <- plot_ly(data, 
               x = ~numDEInCat, y = ~term, 
               type = 'bar',
               name = "term",
               marker = list(colorscale = list(c(0,.5,1), c("brown","gold", "steelblue")),
    reversescale =T,
                             colorbar = list(title = "-log10(FDR)",
                                      len = .8, outlinewidth = 0,
                                      tickformat = ".2f",
                                      tick0 = 0),##, dtick = .01),
                             color = ~Score,
                             line = list(color = "black", width = 1.5)),
    hoverinfo = "text",
    hovertext = paste("Sample:", data$term,
                      "\nGO ID: ", data$category,
                      "\nTotal DE: ", data$numDEInCat,
                      "\nTotal in Cat.: ", data$numInCat,
                      "\nFDR: ", signif(data$adjp, 3))) %>%
    layout(xaxis = list(title = "Number of Genes"),
           yaxis = list(title = ""),
           title = "Top 20 Most Enriched GO Terms",
           margin = m)

@@

go_analysis = GO.data$category[GO.data$adjp <= .05]
scores = setNames(-log10(GO.data$adjp), go_analysis)

simMatrix <- calculateSimMatrix(go_analysis,
                                orgdb="org.Dm.eg.db",
                                ont="BP",
                                method="Rel")

@@

reducedTerms <- reduceSimMatrix(simMatrix,
                                scores,
                                threshold=0.7,
                                orgdb="org.Dm.eg.db")
##write.csv(reducedTerms,"/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/Repressor.BP.reducedTerms.csv")

##simMatrix = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/Repressor.BP.simMatrix.csv", row.names = 1)
##reducedTerms = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/Repressor.BP.reducedTerms.csv", row.names = 1)

### 2023-07-10 TKT_RNAseq/R Code/GO_Analysis.Rmd
update

```{r echo = F, include =F}
##load all files from github
git.dir = "https://raw.githubusercontent.com/johncsantiago/WhartonLab/master/TKT_RNAseq/CountTables/"
cpmdata = read.csv(paste0(git.dir,"TKT_cpmdata.csv"),row.names = 1)
groups  = read.csv(paste0(git.dir,"TKT.metadata.csv"),row.names = 1)
TKT.EdgeR = read.csv(paste0(git.dir,"TKT.EdgeR.Table.csv"),row.names = 1)
GeneIDKey = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/GeneIDKey.csv", row.names = 1)

##CamiData = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/Genes by Df Modifier.csv")

##background = setNames(unique(CamiData$Background), unique(CamiData$Background))

##moderate = setNames(rep(0, length(background)), names(background))

##moderate[unique(CamiData$Moderate)] = 1

##strong = setNames(rep(0, length(background)), names(background))

##strong[unique(CamiData$Strong)] = 1

##lethal = setNames(rep(0, length(background)), names(background))

##lethal[unique(CamiData$Lethal)] = 1

##enhancer = setNames(rep(0, length(background)), names(background))

##enhancer[unique(CamiData$Enhancers)] = 1

##no.effect = setNames(rep(0, length(background)), names(background))

##no.effect[unique(CamiData$No.Effect)] = 1

##FB2Ensembl
##x1=as.list(org.Dm.egENSEMBL2EG)
##Ensembl2Symbol
##x2=as.list(org.Dm.egSYMBOL)
##Symbol2Ensembl
##x3=as.list(org.Dm.egSYMBOL2EG)
##Ensembl2FB
##x4=as.list(org.Dm.egENSEMBL)
##ensembl to FBgn
##x5=as.list(org.Dm.egFLYBASE)

##FBgn2ensembl = row.names(CamiData)
##names(FBgn2ensembl) = row.names(CamiData)
##tempEG = unlist(x1[lengths(x1)==1][row.names(CamiData)])
##FBgn2ensembl[names(tempEG)]=tempEG

##ensembl2symbol = row.names(CamiData)
##names(ensembl2symbol) = FBgn2ensembl
##tempSymbol = unlist(x2[FBgn2ensembl])
##ensembl2symbol[names(tempSymbol)]=tempSymbol
##symbol2ensembl = names(ensembl2symbol)
##names(symbol2ensembl) = ensembl2symbol

##write.csv(names(symbol2ensembl)[grep("FBgn", names(symbol2ensembl))], "/Users/johncsantiago/Documents/CamiExtraGenes.csv")

##extras = read.csv("/Users/johncsantiago/Downloads/FlyBase_Symbol_download.csv", row.names = 1)
##ensembl2symbol[row.names(extras)] = extras$SYMBOL

##symbol = ensembl2symbol

##symbol = background

##symbol[intersect(GeneIDKey$FBgn, background)] = 
##  GeneIDKey[intersect(GeneIDKey$FBgn, background), "Symbol"]

##CamiData = data.frame(FBgn       = background[1:14674],
##                      Symbol     = symbol[1:14674],
##                      Moderate   = moderate[1:14674],
##                      Strong     = strong[1:14674],
##                      Lethal     = lethal[1:14674],
##                      Enhancer   = enhancer[1:14674],
##                      No.Effect  = no.effect[1:14674])

##write.csv(CamiData, "/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/DeficiencyModifierGenes.csv")

Df.data = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/DeficiencyModifierGenes.csv", row.names = 1)

@@

kegg=keggLink("pathway","dme")
names(kegg)=gsub("dme:Dmel_","",names(kegg))

##write.csv(kegg.names, "/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/KEGG.names.csv")
kegg.names = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/KEGG.names.csv", row.names = 1)

temp = setNames(GeneIDKey$Symbol, GeneIDKey$CG)
temp = temp[intersect(names(kegg),names(temp))]
kegg = kegg[intersect(names(kegg),names(temp))]
names(kegg) = temp[names(kegg)]
kegg = as.list(kegg)
keggID=keggConv("dme","ncbi-geneid")

##sigs = Df.data[Df.data$Strong == 1 | Df.data$Moderate == 1 , "Symbol"]
##genes = setNames(rep(0, nrow(Df.data)), Df.data$Symbol)
##genes[sigs] = 1
##pwf=nullp(genes,"dm3","geneSymbol")
##GO.wall=goseq(pwf,"dm3","geneSymbol")
##GO.wall$adjp=p.adjust(GO.wall$over_represented_pvalue,method="BH")
##row.names(GO.wall) = GO.wall$category
##Repress.GO = GO.wall
##write.csv(Repress.GO, "/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/RepressorGOAnalysis.csv")

##KEGG term enrichment is KEGG
##KEGG=goseq(pwf,gene2cat=kegg)
##KEGG$adjp=p.adjust(KEGG$over_represented_pvalue,method="BH")
##row.names(KEGG)=substr(as.character(KEGG[,1]),6,13)
##KEGG$Name=kegg.names[row.names(KEGG),1]
##Repress.KEGG = KEGG
##write.csv(Repress.KEGG, "/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/RepressorKEGGAnalysis.csv")

##sigs = Df.data[Df.data$Lethal == 1, "Symbol"]
##genes = setNames(rep(0, nrow(Df.data)), Df.data$Symbol)
##genes[sigs] = 1
##pwf=nullp(genes,"dm3","geneSymbol")
##GO.wall=goseq(pwf,"dm3","geneSymbol")
##GO.wall$adjp=p.adjust(GO.wall$over_represented_pvalue,method="BH")
##row.names(GO.wall) = GO.wall$category
##Lethal.GO = GO.wall
##write.csv(Lethal.GO, "/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/LethalGOAnalysis.csv")

##KEGG term enrichment is KEGG
##KEGG=goseq(pwf,gene2cat=kegg)
##KEGG$adjp=p.adjust(KEGG$over_represented_pvalue,method="BH")
##row.names(KEGG)=substr(as.character(KEGG[,1]),6,13)
##KEGG$Name=kegg.names[row.names(KEGG),1]
##Lethal.KEGG = KEGG
##write.csv(Lethal.KEGG, "/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/LethalKEGGAnalysis.csv")

##sigs = Df.data[Df.data$Enhancer == 1, "Symbol"]
##genes = setNames(rep(0, nrow(Df.data)), Df.data$Symbol)
##genes[sigs] = 1
##pwf=nullp(genes,"dm3","geneSymbol")
##GO.wall=goseq(pwf,"dm3","geneSymbol")
##GO.wall$adjp=p.adjust(GO.wall$over_represented_pvalue,method="BH")
##row.names(GO.wall) = GO.wall$category
##Enhance.GO = GO.wall
##write.csv(Enhance.GO, "/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/EnhancerGOAnalysis.csv")

##KEGG term enrichment is KEGG
##KEGG=goseq(pwf,gene2cat=kegg)
##KEGG$adjp=p.adjust(KEGG$over_represented_pvalue,method="BH")
##row.names(KEGG)=substr(as.character(KEGG[,1]),6,13)
##EGG$Name=kegg.names[row.names(KEGG),1]
##Enhance.KEGG = KEGG
##write.csv(Enhance.KEGG, "/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/EnhancerKEGGAnalysis.csv")

Repress.GO = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/RepressorGOAnalysis.csv", row.names = 1)
Lethal.GO = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/LethalGOAnalysis.csv", row.names = 1)
Enhance.GO = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/EnhancerGOAnalysis.csv", row.names = 1)

Repress.KEGG = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/RepressorKEGGAnalysis.csv", row.names = 1)
Lethal.KEGG = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/LethalKEGGAnalysis.csv", row.names = 1)
Enhance.KEGG = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/EnhancerKEGGAnalysis.csv", row.names = 1)

@@

```{r}

PathwayID = "04141"

@@

Moderate = Df.data[Df.data$Moderate == 1, "Symbol"]
Moderate = intersect(Moderate, all.path)
Moderate = paste("Dmel_", GeneIDKey[GeneIDKey$Symbol %in% Moderate, "CG"],sep="")

Strong = Df.data[Df.data$Strong == 1, "Symbol"]
Strong = intersect(Strong, all.path)
Strong = paste("Dmel_", GeneIDKey[GeneIDKey$Symbol %in% Strong, "CG"],sep="")

Enhancer = Df.data[Df.data$Enhancer == 1, "Symbol"]
Enhancer = intersect(Enhancer, all.path)
Enhancer = paste("Dmel_", GeneIDKey[GeneIDKey$Symbol %in% Enhancer, "CG"],sep="")

Lethal = Df.data[Df.data$Lethal == 1, "Symbol"]
Lethal = intersect(Lethal, all.path)
Lethal = paste("Dmel_", GeneIDKey[GeneIDKey$Symbol %in% Strong, "CG"],sep="")

@@

knitr::include_graphics(paste0("/Users/johncsantiago/Documents/GitHub/WhartonLab/dme04141.", kegg.names[paste0("dme", PathwayID),1], ".png"))

@@

@@

##reducedTerms <- reduceSimMatrix(simMatrix,
##                                scores,
##                                threshold=0.7,
##                                orgdb="org.Dm.eg.db")
##write.csv(reducedTerms,"/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/Repressor.BP.reducedTerms.csv")

simMatrix = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/Repressor.BP.simMatrix.csv", row.names = 1)
reducedTerms = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/Repressor.BP.reducedTerms.csv", row.names = 1)

>>>>

```{r echo = F, include =F}
##load all files from github
git.dir = "https://raw.githubusercontent.com/johncsantiago/WhartonLab/master/TKT_RNAseq/CountTables/"
cpmdata = read.csv(paste0(git.dir,"TKT_cpmdata.csv"),row.names = 1)
groups  = read.csv(paste0(git.dir,"TKT.metadata.csv"),row.names = 1)
TKT.EdgeR = read.csv(paste0(git.dir,"TKT.EdgeR.Table.csv"),row.names = 1)
GeneIDKey = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/GeneIDKey.csv", row.names = 1)
kegg.names = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/KEGG.names.csv", row.names = 1)
kegg = readRDS("/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/kegg.symbol2path.RData")

##write.csv(kegg.names, "/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/KEGG.names.csv")

keggID=keggConv("dme","ncbi-geneid")

@@

sigs = GeneIDKey[row.names(TKT.EdgeR)[TKT.EdgeR$GRF.CxDf <= .05], "Symbol"]
sigs = GeneIDKey[intersect(row.names(TKT.EdgeR)[TKT.EdgeR$GRF.CxDf <= .05],
                           row.names(cpmdata)[apply(cpmdata[,c("GR.F1","GR.F2","TktDfGR.F1","TktDfGR.F2","TktDfGR.F3")], 1, min) >5]), 
                           "Symbol"]
genes = setNames(rep(0, nrow(TKT.EdgeR)), GeneIDKey[row.names(TKT.EdgeR), "Symbol"])
genes[sigs] = 1
pwf=nullp(genes,"dm3","geneSymbol")
GO.wall=goseq(pwf,"dm3","geneSymbol")
GO.wall$adjp=p.adjust(GO.wall$over_represented_pvalue,method="BH")
row.names(GO.wall) = GO.wall$category
GRF.CxDf.GO = GO.wall
write.csv(GRF.CxDf.GO, "/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq//DataFiles/GRF.CxDf.GOAnalysis.csv")

##KEGG term enrichment is KEGG
KEGG=goseq(pwf,gene2cat=kegg)
KEGG$adjp=p.adjust(KEGG$over_represented_pvalue,method="BH")
row.names(KEGG)=substr(as.character(KEGG[,1]),6,13)
KEGG$Name=kegg.names[row.names(KEGG),1]
GRF.CxDf.KEGG = KEGG
write.csv(GRF.CxDf.KEGG, "/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/DataFiles/GRF.CxDf.KEGGAnalysis.csv")

sigs = GeneIDKey[row.names(TKT.EdgeR)[TKT.EdgeR$GRF.CxDf <= .05], "Symbol"]
sigs = GeneIDKey[intersect(row.names(TKT.EdgeR)[TKT.EdgeR$GRF.CxDf <= .05],
                           row.names(cpmdata)[apply(cpmdata[,c("GR.F1","GR.F2","TktDfGR.F1","TktDfGR.F2","TktDfGR.F3")], 1, min) >5]), 
                           "Symbol"]
genes = setNames(rep(0, nrow(TKT.EdgeR)), GeneIDKey[row.names(TKT.EdgeR), "Symbol"])
genes[sigs] = 1
pwf=nullp(genes,"dm3","geneSymbol")
GO.wall=goseq(pwf,"dm3","geneSymbol")
GO.wall$adjp=p.adjust(GO.wall$over_represented_pvalue,method="BH")
row.names(GO.wall) = GO.wall$category
GRF.CxDf.GO = GO.wall
write.csv(GRF.CxDf.GO, "/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq//DataFiles/GRF.CxDf.GOAnalysis.csv")

##KEGG term enrichment is KEGG
KEGG=goseq(pwf,gene2cat=kegg)
KEGG$adjp=p.adjust(KEGG$over_represented_pvalue,method="BH")
row.names(KEGG)=substr(as.character(KEGG[,1]),6,13)
KEGG$Name=kegg.names[row.names(KEGG),1]
GRF.CxDf.KEGG = KEGG
write.csv(GRF.CxDf.KEGG, "/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/DataFiles/GRF.CxDf.KEGGAnalysis.csv")

@@

GO.data = GRF.CxDf.GO
GO.data = GO.data[GO.data$ontology == 'BP',
                  c("category", "term","adjp", "numDEInCat", "numInCat")]

data = GO.data[20:1,c("term","adjp","numDEInCat", "numInCat", "category")]
data$Score = -log10(data$adjp)
data$term = factor(data$term, levels = c(unique(data$term)))

fig <- plot_ly(data, 
               x = ~numDEInCat, y = ~term, 
               type = 'bar',
               name = "term",
               marker = list(colorscale = list(c(0,.5,1), c("brown","gold", "steelblue")),
    reversescale =T,
                             colorbar = list(title = "-log10(FDR)",
                                      len = .8, outlinewidth = 0,
                                      tickformat = ".2f",
                                      tick0 = 0),##, dtick = .01),
                             color = ~Score,
                             line = list(color = "black", width = 1.5)),
    hoverinfo = "text",
    hovertext = paste("Sample:", data$term,
                      "\nGO ID: ", data$category,
                      "\nTotal DE: ", data$numDEInCat,
                      "\nTotal in Cat.: ", data$numInCat,
                      "\nFDR: ", signif(data$adjp, 3))) %>%
    layout(xaxis = list(title = "Number of Genes"),
           yaxis = list(title = ""),
           title = "Top 20 Most Enriched GO Terms",
           margin = m)

```{r, echo = F, include = F}

KEGG20 = function(data){

  data = data[1:20, c("category", "Name","adjp", "numDEInCat", "numInCat")]

data = data[20:1,]
data$Score = -log10(data$adjp)
data$term = factor(data$Name, levels = c(unique(data$Name)))

fig <- plot_ly(data, 
               x = ~numDEInCat, y = ~term, 
               type = 'bar',
               name = "Name",
               marker = list(colorscale = list(c(0,.5,1), c("brown","gold", "steelblue")),
    reversescale =T,
                             colorbar = list(title = "-log10(FDR)",
                                      len = .8, outlinewidth = 0,
                                      tickformat = ".2f",
                                      tick0 = 0),##, dtick = .01),
                             color = ~Score,
                             line = list(color = "black", width = 1.5)),
    hoverinfo = "text",
    hovertext = paste("Sample:", data$Name,
                      "\nGO ID: ", data$category,
                      "\nTotal DE: ", data$numDEInCat,
                      "\nTotal in Cat.: ", data$numInCat,
                      "\nFDR: ", signif(data$adjp, 3))) %>%
    layout(xaxis = list(title = "Number of Genes"),
           yaxis = list(title = ""),
           title = "Top 20 Most Enriched KEGG Terms",
           margin = m)

return(fig)

}

```{r fig.width=10}

data = GRF.CxDf.KEGG

KEGG20(data)

```{r echo = F, include = F}
PathwayID = "03050"

@@

Df = GeneIDKey[intersect(row.names(TKT.EdgeR)[TKT.EdgeR$GRF.CxDf <= .05],
                         row.names(cpmdata)[apply(cpmdata[,c("GR.F1","GR.F2","TktDfGR.F1","TktDfGR.F2","TktDfGR.F3")], 1, min) >5]), 
                         "Symbol"]
Df = intersect(Df, all.path)
Df = paste("Dmel_", GeneIDKey[GeneIDKey$Symbol %in% Df, "CG"],sep="")

OE = GeneIDKey[intersect(row.names(TKT.EdgeR)[TKT.EdgeR$GRF.CxOE <= .05],
                         row.names(cpmdata)[apply(cpmdata[,c("GR.F1","GR.F2","TktOEGR.F1","TktOEGR.F2","TktOEGR.F3")], 1, min) >5]), 
                         "Symbol"]
OE = intersect(OE, all.path)
OE = paste("Dmel_", GeneIDKey[GeneIDKey$Symbol %in% OE, "CG"],sep="")

@@

@@

```{r}
knitr::include_graphics(paste0("/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/dme",PathwayID, ".", kegg.names[paste0("dme", PathwayID),1], ".png"))
```

@@

reducedTerms <- reduceSimMatrix(simMatrix,
                                scores,
                                threshold=0.7,
                                orgdb="org.Dm.eg.db")
##write.csv(reducedTerms,"/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/Repressor.BP.reducedTerms.csv")

##simMatrix = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/Repressor.BP.simMatrix.csv", row.names = 1)
##reducedTerms = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/Repressor.BP.reducedTerms.csv", row.names = 1)
